---
title: "Final Paper"
author: "STOR 320(1) Group 5"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---
```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(tidyverse)
library(readr)
library(dplyr)
library(RColorBrewer)
library(purrr)
library(zipcode)
library(ggplot2)
library(sf)
library(modelr)
library(lubridate)
library(data.table)
library(ggrepel)
library(ggmap)
library(date)
library(readxl)
library(plotrix)
library(xtable)
library(caret)

CAMAR <- read_csv("FinalProject/ResidentialApprasials.csv")
AP <- read_csv("FinalProject/Address_Points.csv")
ZCS <- read_csv("FinalProject/ZipCodeStats.csv")
businesses <- read_csv("FinalProject/Businesses.csv")
census2010 <- read_csv("FinalProject/Census_Tracts_in_2010.csv")
hospitals <- read_csv("FinalProject/localHospitals.csv")
quickFacts<- read_csv("FinalProject/DC.quickfacts.csv")
FS<-read_csv("FinalProject/Fire_Stations.csv")
TaxLotsHistorical <- read_csv("FinalProject/TaxLots.csv")

geoidfix <- read_excel("FinalProject/geoidfix.xlsx")
geoidtozip <- read_excel("FinalProject/geoid-to-zip.xlsx")
incomedata<- read_excel("FinalProject/DCincomedata.xlsx")

modeling<-read_excel("FinalProject/leftismodel1rightismodel2.xlsx")

#google maps datasets
incidents= read.csv('https://raw.githubusercontent.com/lgellis/MiscTutorial/master/ggmap/i2Sample.csv', stringsAsFactors = FALSE)
n <- read.csv('https://raw.githubusercontent.com/lgellis/MiscTutorial/master/ggmap/n.csv', stringsAsFactors = FALSE)
```
#Data Tidying 
```{r,echo=FALSE,warning=FALSE,message=FALSE}
CAMAR %>%
  select(SSL)

separate(CAMAR, SSL, c("Square Suffix", "Lot"))

AP1 <- AP %>%
  select(SSL, SQUARE, LOT, SUFFIX, XCOORD, YCOORD, ZIPCODE, ZIPCODE4, LATITUDE, LONGITUDE)

CAMAR = CAMAR %>%
  left_join(AP1, by = "SSL")

CAMAR <- select(CAMAR, SSL, PRICE,SQUARE, XCOORD, YCOORD, ZIPCODE, LATITUDE, LONGITUDE)
CAMAR <- filter(CAMAR, PRICE>0, ZIPCODE>0)

```
#code for google maps
```{r,echo=FALSE,warning=FALSE,message=FALSE}
dim(incidents)
attach(incidents)
dim(n)
attach(n)

col1 = "#011f4b"
col2 = "#6497b1"
col3 = "#b3cde0"
col4 = "#CC0000"

#add year to the incidents data frame
incidents$ymd <-mdy_hms(Event.Clearance.Date)
incidents$year <- year(incidents$ymd)

#Create a more manageable data frame with only 2017 and 2018 data
i2 <- incidents %>% 
  filter(year>=2017 & year<=2018)

#Only include complete cases
i2[complete.cases(i2), ]

#create a display label to the n data frame (dangerous neighbourhoods)
n$label <-paste(Rank, Location, sep="-")

#Set your API Key
ggmap::register_google(key = "AIzaSyDTKye0LUc2XdfHpetmV9KKikRuThlyviM")


DC <- ggmap(get_googlemap(center = c(lon = -77.025, lat =  38.9072),
                    zoom = 12, scale = 1,
                    maptype ='hybrid',
                    color = 'color'))
```
#made a new variable based on categories of price, ggplot to show
```{r,echo=FALSE,warning=FALSE,message=FALSE}
priceRanges <- mutate(CAMAR, PRICERANGE=

ifelse(PRICE %in% 1:250000, "1. 250,000 or less",

ifelse(PRICE %in% 250000:500000, "2. 250,000 to 500,000",

ifelse(PRICE %in% 500000:750000, "3. 500,000 to 750,000",

ifelse(PRICE %in% 750000:1000000, "4. 750,000 to 1 million",

ifelse(PRICE %in% 1000000:5000000, "5. 1 to 5 million", "Over 5 million"))))))

DC + geom_point(aes(x = LONGITUDE, y = LATITUDE, color=PRICERANGE), data = priceRanges, size = .5) + 
theme(legend.position="right") +
scale_color_brewer(palette = "YlOrRd")
```
#make table of price summary statistics per zip code
```{r,echo=FALSE,warning=FALSE,message=FALSE}
CAMAR
priceSummary<-CAMAR %>%
  select(PRICE, ZIPCODE) %>%
  group_by(ZIPCODE)
```
#chunk on zip code stats(uninsured, medicaid recipients per zip code)
```{r,echo=FALSE,warning=FALSE,message=FALSE}
Z<-select(ZCS, ZIPCODE, UNINSURED_POPULATION, MEDICAID_RECIPIENT)

Z <- CAMAR%>%
  left_join(Z, by="ZIPCODE")

Z<- select(Z, PRICE, ZIPCODE, UNINSURED_POPULATION, MEDICAID_RECIPIENT)

Z<-rename(Z, UNINSURED=UNINSURED_POPULATION, MEDICAID=MEDICAID_RECIPIENT)
Z<- Z[!duplicated(Z$ZIPCODE),]
```
#local hospitals, emergency centers, firestations
```{r,echo=FALSE,warning=FALSE,message=FALSE}
#HOSPITALS
hospital<-filter(hospitals, STATE=="DC")
hospital<-select(hospital,ZIP,X,Y,ADDRESS)
hospital<-rename(hospital, ZIPCODE=ZIP)
camarDistinctZip<-distinct(CAMAR,ZIPCODE)
#dataset on hospital details
hospital <- hospital%>%
  left_join(camarDistinctZip, by="ZIPCODE") 
#dataset showing number of hospitals in each zipcode
hospitalsPerZip<- count(hospital,ZIPCODE)
hospitalsPerZip<-rename(hospitalsPerZip,"Number of Hospitals"=n)
hospitalsPerZip<-arrange(hospitalsPerZip, ZIPCODE)
#ds is a dataset on fire station details
fs<-filter(FS, STATE=="DC")
fs<-select(fs, ZIP, X, Y, ADDRESS)
fs<-rename(fs, ZIPCODE=ZIP)
fs <- fs %>% 
  left_join(camarDistinctZip, by="ZIPCODE")
#dataset showing number of hospitals in each zipcode
fsPerZip<-count(fs, ZIPCODE)
fsPerZip<-rename(fsPerZip,"Number of Fire Stations"=n)
fsPerZip<-arrange(fsPerZip, ZIPCODE)
#dataset showing number of hospitals and fire stations 
totalNumHFS<- fsPerZip %>%
  full_join(hospitalsPerZip)
totalNumHFS[is.na(totalNumHFS)]<-0
totalNumHFS<- filter(totalNumHFS, ZIPCODE<=20052)
```
#taxable income based off gross income categories per zipcode
```{r,echo=FALSE,warning=FALSE,message=FALSE}
incomestats<-incomedata[6:212,]
incomestats<-select(incomestats,"DISTRICT OF COLUMBIA", "...2","...76","...94","...136")
incomestats<-rename(incomestats, "zip"="DISTRICT OF COLUMBIA", "gross income" = "...2", "Returns for total taxes" = "...76","Returns for taxable income" = "...94", "Returns for income tax"="...136")
taxableincome<-incomestats[,c(1,2,5)]
taxableincome<-filter(taxableincome, zip >-1)
taxableincome[is.na(taxableincome)]<-'Total'
taxableincome<- mutate(taxableincome, 'Total', 20001,20002,20003,20003,20005,20007,20008,20009,20010,20010,20011,20012,20015,20016,20017,20018,20019,20020,20024,20032,20036,20037)
taxableincomeB<-taxableincome[1:7,]
taxableincomeB[c(4)]=taxableincome[1:7,c(3)]
taxableincomeB[c(5)]=taxableincome[8:14,c(3)]
taxableincomeB[c(6)]=taxableincome[15:21,c(3)]
taxableincomeB[c(7)]=taxableincome[22:28,c(3)]
taxableincomeB[c(8)]=taxableincome[29:35,c(3)]
taxableincomeB[c(9)]=taxableincome[36:42,c(3)]
taxableincomeB[c(10)]=taxableincome[43:49,c(3)]
taxableincomeB[c(11)]=taxableincome[50:56,c(3)]
taxableincomeB[c(12)]=taxableincome[57:63,c(3)]
taxableincomeB[c(13)]=taxableincome[64:70,c(3)]
taxableincomeB[c(14)]=taxableincome[71:77,c(3)]
taxableincomeB[c(15)]=taxableincome[78:84,c(3)]
taxableincomeB[c(16)]=taxableincome[85:91,c(3)]
taxableincomeB[c(17)]=taxableincome[92:98,c(3)]
taxableincomeB[c(18)]=taxableincome[99:105,c(3)]
taxableincomeB[c(19)]=taxableincome[106:112,c(3)]
taxableincomeB[c(20)]=taxableincome[113:119,c(3)]
taxableincomeB[c(21)]=taxableincome[120:126,c(3)]
taxableincomeB[c(22)]=taxableincome[127:133,c(3)]

taxableincomeB<-select(taxableincomeB,-zip,-"Returns for income tax")
taxableincomeB[2:22]<-lapply(taxableincomeB[2:22],as.numeric)
```
#Get Percent By Zip Function
```{r,echo=FALSE,warning=FALSE,message=FALSE}
getPercentbyZip<- function(zipcode) {
x= which(colnames(taxableincomeB)==zipcode)
a=as.numeric(taxableincomeB[2,x])
b=as.numeric(taxableincomeB[3,x])
c=as.numeric(taxableincomeB[4,x])
d=as.numeric(taxableincomeB[5,x])
e=as.numeric(taxableincomeB[6,x])
f=as.numeric(taxableincomeB[7,x])
df=c(a,b,c,d,e,f)
max=0
Gross_Income = ""
for(i in seq_along(df)) {
if(df[[i]] > max){
max = df[[i]]
}
if(df[[i]]==max){
}}
category=taxableincomeB[which(taxableincomeB[,x]==max),1]
if( nrow(category) > 1)
category[2,1]
if(nrow(category)==1)
category
}#end function
Zipcodes = CAMAR %>%
select(ZIPCODE) %>%
distinct(ZIPCODE) %>%
arrange(ZIPCODE) %>%
mutate(Gross_Income="")
Zipcodes<-Zipcodes[1:20,]

Zipcodes[1,2]="$100,000 under $200,000"
Zipcodes[2,2]=getPercentbyZip(20002)
Zipcodes[3,2]=getPercentbyZip(20003)
Zipcodes[4,2]=getPercentbyZip(20005)
Zipcodes[5,2]=getPercentbyZip(20007)
Zipcodes[6,2]=getPercentbyZip(20008)
Zipcodes[7,2]=getPercentbyZip(20009)
Zipcodes[8,2]=getPercentbyZip(20010)
Zipcodes[9,2]=getPercentbyZip(20011)
Zipcodes[10,2]=getPercentbyZip(20012)
Zipcodes[11,2]=getPercentbyZip(20015)
Zipcodes[12,2]=getPercentbyZip(20016)
Zipcodes[13,2]=getPercentbyZip(20017)
Zipcodes[14,2]=getPercentbyZip(20018)
Zipcodes[15,2]=getPercentbyZip(20019)
Zipcodes[16,2]=getPercentbyZip(20020)
Zipcodes[17,2]=getPercentbyZip(20024)
Zipcodes[18,2]=getPercentbyZip(20032)
Zipcodes[19,2]=getPercentbyZip(20036)
Zipcodes[20,2]=getPercentbyZip(20037)
GIpercents<-count(Zipcodes,Gross_Income)
GIpercents <- mutate(GIpercents, Percentages=n/20)
GIpercents<- arrange(GIpercents,Gross_Income)
GIpercents<- rename(GIpercents, "Gross Income Levels"="Gross_Income")
```
#mean ranges
```{r,echo=FALSE,warning=FALSE,message=FALSE}
meanRanges <- mutate(CAMAR.MEAN, MEANRANGE=
ifelse(floor(mean) %in% 1:250000, "1. 250,000 or less",
ifelse(floor(mean) %in% 250000:500000, "2. 250,000 to 500,000",
ifelse(floor(mean) %in% 500000:750000, "3. 500,000 to 750,000",
ifelse(floor(mean) %in% 750000:1000000, "4. 750,000 to 1 million",
ifelse(floor(mean) %in% 1000000:5000000, "5. 1 to 5 million", "6. Over 5 million"))))))
```
#foreign born population
```{r,echo=FALSE,warning=FALSE,message=FALSE}
TOTALPOPULATIONCHAR=select(CAMAR_dem,PRICERANGE,PRICE,Tract10, ZIPCODE, LATITUDE, LONGITUDE, GEOID, pct_TotPopACS17, pct_TotPopinHHs, pct_TotUnder5, pct_Hispanic, pct_BlackAloneOrCombo, pct_AmerIndAloneorCombo, pct_AsianAloneOrCombo, pct_NatHawAloneOrCombo, 	
pct_WhiteAloneOrCombo)%>%
  group_by(LATITUDE, LONGITUDE)

FOREIGNBORNPOP <- CAMAR_dem %>%
  select(PRICERANGE,PRICE,Tract10, ZIPCODE, LATITUDE, LONGITUDE, GEOID, pct_TotPopBornOutUS_TotPop, pct_TotPopBornOutUS, pct_FB2010Plus, pct_FB2000Plus, pct_FBNotCit2010Plus, pct_FBNotCit2000Plus) %>%
```
#race
```{r,echo=FALSE,warning=FALSE,message=FALSE}
TP <- TOTALPOPULATIONCHAR %>%
  group_by(LATITUDE, LONGITUDE, ZIPCODE) %>%
  summarize_at(vars(pct_Hispanic, pct_BlackAloneOrCombo, pct_AmerIndAloneorCombo, pct_AsianAloneOrCombo, pct_NatHawAloneOrCombo, pct_WhiteAloneOrCombo), mean, na.rm=TRUE)
TP2 <- TOTALPOPULATIONCHAR %>%
  group_by(ZIPCODE) %>%
  summarize_at(vars(pct_Hispanic, pct_BlackAloneOrCombo, pct_AmerIndAloneorCombo, pct_AsianAloneOrCombo, pct_NatHawAloneOrCombo, pct_WhiteAloneOrCombo), mean, na.rm=TRUE)
TP2 <- TP %>%
  mutate(DIVERSE =
  ifelse(pct_WhiteAloneOrCombo >= .5 | pct_BlackAloneOrCombo>= .5  | pct_Hispanic >= .5 | pct_AmerIndAloneorCombo >= .5  | pct_AsianAloneOrCombo >= .5  | pct_NatHawAloneOrCombo >= .5, "no", "yes")
  )
TP4 <- TOTALPOPULATIONCHAR %>%
  group_by(LATITUDE, LONGITUDE, ZIPCODE, PRICE) %>%
  summarize_at(vars(pct_Hispanic, pct_BlackAloneOrCombo, pct_AmerIndAloneorCombo, pct_AsianAloneOrCombo, pct_NatHawAloneOrCombo, pct_WhiteAloneOrCombo), mean, na.rm=TRUE)

TP5 <- TP4 %>%
  mutate(
    PRICE_propW= PRICE*pct_WhiteAloneOrCombo,
    PRICE_propB= PRICE*pct_BlackAloneOrCombo
         ) %>%
  ungroup(LATITUDE, LONGITUDE, ZIPCODE, PRICE)

priceRangesProp <- mutate(TP5, PRICERANGEW=
ifelse(PRICE_propW <= 250000, "1. 250,000 or less",
ifelse(PRICE_propW <= 500000, "2. 250,000 to 500,000",
ifelse(PRICE_propW <= 750000, "3. 500,000 to 750,000",
ifelse(PRICE_propW <= 1000000, "4. 750,000 to 1 million",
ifelse(PRICE_propW <= 5000000, "5. 1 to 5 million",
ifelse(PRICE_propW <= 10000000, "6. 5 to 10 million",
ifelse(PRICE_propW <= 20000000, "7. 10 to 20 million", "8. over 20 million"))))))), 

PRICERANGEB=
ifelse(PRICE_propB <= 250000, "1. 250,000 or less",
ifelse(PRICE_propB <= 500000, "2. 250,000 to 500,000",
ifelse(PRICE_propB <= 750000, "3. 500,000 to 750,000",
ifelse(PRICE_propB <= 1000000, "4. 750,000 to 1 million",
ifelse(PRICE_propB <= 5000000, "5. 1 to 5 million",
ifelse(PRICE_propB <= 10000000, "6. 5 to 10 million",
ifelse(PRICE_propB <= 20000000, "7. 10 to 20 million", "8. over 20 million")))))))
)
```
#poverty
```{r,echo=FALSE,warning=FALSE,message=FALSE}
POVERTY <- CAMAR_dem %>%
    select(PRICERANGE, PRICE, Tract10, ZIPCODE, LATITUDE, LONGITUDE, GEOID, pct_Poverty_TOTAL, pct_Poverty_Less100, pct_Poverty_Less150, pct_Poverty_Less200) %>%
  group_by(ZIPCODE)

POV1 <- POVERTY %>%
  group_by(ZIPCODE, LATITUDE, LONGITUDE, PRICE) %>%
  summarize_at(vars(pct_Poverty_TOTAL, pct_Poverty_Less100, pct_Poverty_Less150, pct_Poverty_Less200), mean, na.rm=TRUE)


POV2<- POV1 %>%
  mutate(
    PRICEvPOV = PRICE * pct_Poverty_TOTAL
  )
priceRangesPOV <- mutate(POV2, PRICERANGEPOV=
ifelse(PRICEvPOV <= 250000, "1. 250,000 or less",
ifelse(PRICEvPOV <= 500000, "2. 250,000 to 500,000",
ifelse(PRICEvPOV <= 750000, "3. 500,000 to 750,000",
ifelse(PRICEvPOV <= 1000000, "4. 750,000 to 1 million",
ifelse(PRICEvPOV <= 5000000, "5. 1 to 5 million",
ifelse(PRICEvPOV <= 10000000, "6. 5 to 10 million",
ifelse(PRICEvPOV <= 20000000, "7. 10 to 20 million", "8. over 20 million"))))))))
```
#plots we are using for final paper:
```{r,echo=FALSE,warning=FALSE,message=FALSE}
#price range and poverty distribution
DC + geom_point(aes(x = LONGITUDE, y = LATITUDE, color=PRICERANGEPOV), data = priceRangesPOV, size = .5) + 
  theme(legend.position="right") +
  ggtitle("Price Range and Poverty Distribution of DC")
scale_color_brewer(palette = "RdPu")

#bar and pie charts on Gross Income Levels
bp<- ggplot(GIpercents, aes(x="", y=Percentages, fill=`Gross Income Levels`))+
geom_bar(width = 1, stat = "identity")
pie<-bp+coord_polar("y",start=0)
bp
pie

#mean prices of house based on zipcode
DC + geom_point(aes(x = LONGITUDE, y = LATITUDE, color=MEANRANGE), data = meanRanges, size = .5) + 
theme(legend.position="right") +
scale_color_brewer(palette = "YlOrRd") +
xlab("Longitude")+
ylab("Latitude")+
ggtitle("Mean Price of Houses Based on Zipcode")

ZIP.MEAN <- ggplot(data=CAMAR.MEAN, mapping = aes(x = LATITUDE, y = LONGITUDE, color=mean)) +
geom_point()+
xlab("Longitude")+
ylab("Latitude")+
ggtitle("Mean Price of Houses Based on Zipcode")
ZIP.MEAN

#race concentration
DC +   geom_point(aes(x = LONGITUDE, y = LATITUDE, color = pct_WhiteAloneOrCombo), data = TP, alpha=0.25, size = 0.5) + 
  theme(legend.position="none")+
xlab("Longitude")+
ylab("Latitude")+
ggtitle("Concentration of Whites Based on Location")

DC+  geom_point(aes(x = LONGITUDE, y = LATITUDE, color = pct_BlackAloneOrCombo), data = TP, alpha=0.25, size = 0.5) + 
  theme(legend.position="none")+
xlab("Longitude") +
ylab("Latitude") +
ggtitle("Concentration of Blacks Based on Location") 

DC + geom_point(aes(x = LONGITUDE, y = LATITUDE, color = as.factor(DIVERSE)), data = TP2, alpha=0.25, size = 0.5) 

#table on zip code healthcare statistics
zipStats

##business enterprise graph- needs work lol
DC + 
  geom_point(aes(x = LONGITUDE, y = LATITUDE,col="red"), data = businesses, size = .5) 

#plot on price ranges of houses
DC + geom_point(aes(x = LONGITUDE, y = LATITUDE, color=PRICERANGE), data = priceRanges, size = .5) + 
theme(legend.position="right") +
scale_color_brewer(palette = "YlOrRd")+
xlab("Longitude")+
ylab("Latitude")+
ggtitle("Price of Houses Based on Geographic Location")

#summary table of pricing data
summary<-summarize(priceSummary,mean=mean(PRICE),sd=sd(PRICE),min=min(PRICE),max=max(PRICE))
meanPriceZip<-select(summary,ZIPCODE,mean)
```
#modeling for healthcare
```{r,echo=FALSE,warning=FALSE,message=FALSE}
CAMAR.ZIP = CAMAR[!duplicated(CAMAR$ZIPCODE),]
CAMAR.ZIP<-select(CAMAR.ZIP, PRICE, ZIPCODE, LATITUDE, LONGITUDE)
CAMAR.ZIP.AVG <- CAMAR.ZIP %>%
group_by(ZIPCODE) %>%
summarize(mean=mean(PRICE))
CAMAR.MEAN = CAMAR.ZIP %>%
left_join(CAMAR.ZIP.AVG, by = "ZIPCODE")
FHSMean <-totalNumHFS %>%
left_join(CAMAR.ZIP.AVG, by = "ZIPCODE")
FHSMeanB <- FHSMean %>%
  full_join(CAMAR)
FHSMeanB<-select(FHSMeanB,"ZIPCODE", "Number of Fire Stations", "Number of Hospitals", "PRICE")
FHSMeanB<-rename(FHSMeanB, "NumberofHospitals" = "Number of Hospitals")
FHSMeanB<-rename(FHSMeanB, "NumberFireStations"="Number of Fire Stations")

HFMod=lm(PRICE~NumberFireStations+NumberofHospitals+NumberFireStations*NumberofHospitals, data=FHSMeanB)
anova(HFMod)
#significant: fire stations, hospitals, interaction between fire stations and hospitals
#significant: uninsured, insignificant: Medicaid
```

```{r,echo=FALSE,warning=FALSE,message=FALSE}
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x))) }

knnc <- as.data.frame(lapply(CAMAR[6:8], normalize))

knnc$Price = CAMAR$PRICE
trControl <- trainControl(method  = "cv", number  = 5)
fit <- train(Price ~ .,
             method     = "knn",
             tuneGrid   = expand.grid(k = 1:20),
             trControl  = trControl,
             data       = knnc)

knnc$Price = CAMAR$PRICE
trControl <- trainControl(method  = "cv", number  = 5)
fit <- train(Price ~ .,
             method     = "knn",
             tuneGrid   = expand.grid(k = 1:20),
             trControl  = trControl,
             data       = knnc)
```

```{r}
#put variables into percentage for use
ZC1 <- ZCS %>%
  mutate(
	per_uninsured=UNINSURED_POPULATION/POP_2000,
	per_medicaid=MEDICAID_RECIPIENT/POP_2000,
  )

ZC1 <- ZC1 %>% select(ZIPCODE, per_uninsured, per_medicaid, POP_2000)

ZC2 <- left_join(TP5, ZC1, by="ZIPCODE")
```


```{r,warning=FALSE,echo=FALSE}
P1 <- DC + geom_point(aes(x = LONGITUDE, y = LATITUDE, color=PRICERANGEW), data = priceRangesProp, size = .5) +
  theme(legend.position="right") +
  ggtitle("Price Range and %White Population Distribution")+
  xlab("Longitude")+
  ylab("Latitude")+
  guides(color=guide_legend(title="House Price")) +
scale_color_brewer(palette = "PuRd")



P2<- DC + geom_point(aes(x = LONGITUDE, y = LATITUDE, color=PRICERANGEB), data = priceRangesProp, size = .5) +
  theme(legend.position="right") +
	ggtitle("Price Range and %Black Population Distribution")+
   xlab("Longitude")+
  ylab("Latitude")+
  guides(color=guide_legend(title="House Price")) +
scale_color_brewer(palette = "PuRd")

```

```{r,warning=FALSE,echo=FALSE}
R1<- DC+  geom_point(aes(x = LONGITUDE, y = LATITUDE, color = pct_WhiteAloneOrCombo), data = TP, alpha=0.25, size = 0.5) +
  theme(legend.position="right") +
  ggtitle("%White Population Distribution of DC")+
xlab("Longitude")+
  ylab("Latitude")+
  guides(color=guide_legend(title="Poverty"))


R2 <- DC+  geom_point(aes(x = LONGITUDE, y = LATITUDE, color = pct_BlackAloneOrCombo), data = TP, alpha=0.25, size = 0.5)+ theme(legend.position="right") +
  ggtitle("%Black Population Distribution of DC")+
xlab("Longitude")+
  ylab("Latitude")+
  guides(color=guide_legend(title="Poverty"))



R3 <- DC + geom_point(aes(x = LONGITUDE, y = LATITUDE, color=pct_Poverty_Less150), data = POV1, size = .5) +
  theme(legend.position="right") +
  ggtitle("Poverty Distribution of DC")+
xlab("Longitude")+
  ylab("Latitude")+
  guides(color=guide_legend(title="Poverty"))

```


```{r,warning=FALSE,echo=FALSE}
DC + geom_point(aes(x = LONGITUDE, y = LATITUDE, color=POP_2000), data = ZC2, size = .5) +
  theme(legend.position="right") +
  ggtitle("Population Distribution of DC in 2000")+
  guides(color=guide_legend(title="Pop"))
```

```{r,warning=FALSE,echo=FALSE}
T1 <- DC + geom_point(aes(x = LONGITUDE, y = LATITUDE, color=per_uninsured), data = ZC2, size = .5) +
  theme(legend.position="right") +
  ggtitle("Uninsured Population Distribution of DC in 2000")+
  guides(color=guide_legend(title="Uninsured"))

T2 <- DC + geom_point(aes(x = LONGITUDE, y = LATITUDE, color=per_medicaid), data = ZC2, size = .5) +
  theme(legend.position="right") +
  ggtitle("Medicaid Distribution of DC in 2000")+
  guides(color=guide_legend(title="Medicaid"))

T3 <-DC + geom_point(aes(x = LONGITUDE, y = LATITUDE, color=POP_2000), data = ZC2, size = .5) +
  theme(legend.position="right") +
  ggtitle("Population Distribution of DC in 2000")+
  guides(color=guide_legend(title="Pop"))

```

```{r,warning=FALSE,echo=FALSE}
DC + geom_point(aes(x = LONGITUDE, y = LATITUDE, color = as.factor(DIVERSE)), data = TP2, alpha=0.25, size = 0.5) +
	theme(legend.position="right") +
  ggtitle("Diversity Distribution of DC")+
xlab("Longitude")+
  ylab("Latitude")+
  guides(color=guide_legend(title="Diversity"))
```
